General purpose gene annotation using deep learning

### 2020-01-08 paper/main.tex
paper results table

\begin{methods}
\section{Methods}
We worked with 192 animal and 60 plant genomes. The data of each genome consists of the latest publically available genomic assembly in form of a FASTA file and the latest annotation in the GFF format. We used all animals genomes in ensembl Metazoa 45 (?) \citealp{Howe19} as well as those of all non-embargoed plant genomes of the JGI Phytosome 13 database (?, citation). Both data groups were used seperately during training as well as during evaluation. At the start of our work we split both genome groups into training and test sets, which then contained 19 or 6 genomes, respectively. Some of the remaining genomes were used for training purposes and all were used for evaluating our models.

@@

>>>>

\begin{methods}
\section{Methods}
We worked with 192 animal and 60 plant genomes. The data of each genome consists of the latest publically available genomic assembly in form of a FASTA file and the latest annotation in the GFF format. We used all animals genomes in EnsemblMetazoa 45 (?) \citealp{Howe19} as well as those of all non-embargoed plant genomes of the JGI Phytosome 13 database (?, citation). Both data groups were used seperately during training as well as during evaluation. At the start of our work we split both genome groups into training and test sets, which then contained 19 or 6 genomes, respectively. Some of the remaining genomes were used for training purposes and all were used for evaluating our models.

@@

\begin{table}[!t]
\processtable{Experimental Results and Comparison\label{Tab:03}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Augustus & 0.62 (+-0.02) & 0.83 (+- 0.03)\\
Best Helixer model & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Best model + varied input length & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Best model + varied input length & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Best model + varied input length + overlapping & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Varied input length + overlapping + ensembling & 0.62 (+-0.02) & 0.72 (+-0.02) \\
\botrule
\end{tabular}}{Values are averages in CDS F1 (?) across all validation and test genomes of the \\ respective group.}
\end{table}
